Decoupled wood and leaf strategies among canopy and understorey tree in a low-elevation rainforest of India

### 2018-07-13 draft.Rmd
Uppangala 0.1.9050 BRIDGE test

---
title: Decoupled wood and leaf strategies among canopy and understorey tree in a low-elevation rainforest of India
author: "Sylvain Schmitt, Valérie Raevel, Maxime Réjou-Méchain, Ayyappan N, Balachandran N., Barathan N., and François Munoz"
date: '`r Sys.Date()`'
output:
  bookdown::word_document2: default
  bookdown::pdf_document2:
    includes:
      before_body: ./template/doc_prefix.tex
      in_header: ./template/preamble.tex
    number_sections: false
    toc: false
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float: yes
linestretch: 1.5
csl: bibliography/mee.csl
bibliography: ["bibliography/refs.bib", "bibliography/library.bib"] 
link-citations: yes
---

@@

```{r PCA,  fig.cap='Principal Component Analysis (PCA) of species mean trait values. Marginal plots represent the density distribution of species on the two principal component axis for each morphotype. See table \\@ref(tab:Traits) for abbreviation.'}
pca.plot <- autoplot(PFT.pca, 
         data = Q %>% 
           left_join(L %>% 
                       dplyr::select(-com) %>% 
                       summarise_all(sum) %>% 
                       t() %>% 
                       data.frame() %>% 
                       rename(abundance =  ".") %>% 
                       mutate(SpCode = row.names(.))) %>% 
           filter(!is.na(WES)), 
         colour = "strata",
         size = "abundance",
         loadings.label.size = 6,
         loadings.label.colour = 'black',
         loadings = T, loadings.label = T, loadings.colour = 'black',
         loadings.label.vjust = 1.2) +
  coord_equal() +
  geom_hline(aes(yintercept = 0), col = 'green', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'purple', linetype = "dotted") +
  xlab('Axe 1 − 33.66 %') + ylab('Axe 2 − 29.07 %') +
  theme(legend.position = c(1, 1), 
        legend.justification = c(1, 1))
spectrum.density <-pca.plot$data %>% 
  select(Comp.1, Comp.2, strata) %>% 
  rename(WES = Comp.1, LES = Comp.2) %>% 
  melt(id.vars = "strata", variable.name = "spectrum") %>% 
  ggplot(aes(value, color = spectrum, fill = spectrum)) +
  geom_density(alpha = 0.5) + 
  facet_wrap(~strata, nrow = 2) +
  coord_flip() +
  scale_fill_manual("PCA axis", 
                    labels = c("WES" = "PCA1", "LES" = "PCA2"),
                    values = c("green", "purple")) +
  scale_color_manual("PCA axis", 
                     labels = c("WES" = "PCA1", "LES" = "PCA2"),
                     values = c("green", "purple"))
cowplot::plot_grid(pca.plot, spectrum.density, rel_widths = c(2,1))
```

@@

**In waiting for BRIDGE dataset.**

>>>>

---
title: Decoupled wood and leaf strategies among canopy and understorey tree in a low-elevation rainforest of India
author: "Sylvain Schmitt, Valérie Raevel, Maxime Réjou-Méchain, Ayyappan N, Balachandran N., Barathan N., and François Munoz"
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: false
    toc: true
    toc_float: yes
  bookdown::pdf_document2:
    includes:
      before_body: ./template/doc_prefix.tex
      in_header: ./template/preamble.tex
    number_sections: false
    toc: false
  bookdown::word_document2: default
linestretch: 1.5
csl: bibliography/mee.csl
bibliography: ["bibliography/refs.bib", "bibliography/library.bib"] 
link-citations: yes
---

@@

```{r PCA,  fig.cap='Principal Component Analysis (PCA) of species mean trait values. Marginal plots represent the density distribution of species on the two principal component axis for each strata. See table \\@ref(tab:Traits) for abbreviation.'}
pca.plot <- autoplot(PFT.pca, 
         data = Q %>% 
           left_join(L %>% 
                       dplyr::select(-com) %>% 
                       summarise_all(sum) %>% 
                       t() %>% 
                       data.frame() %>% 
                       rename(abundance =  ".") %>% 
                       mutate(SpCode = row.names(.))) %>% 
           filter(!is.na(WES)), 
         colour = "strata",
         size = "abundance",
         loadings.label.size = 6,
         loadings.label.colour = 'black',
         loadings = T, loadings.label = T, loadings.colour = 'black',
         loadings.label.vjust = 1.2) +
  coord_equal() +
  geom_hline(aes(yintercept = 0), col = 'green', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'purple', linetype = "dotted") +
  xlab('Axe 1 − 33.66 %') + ylab('Axe 2 − 29.07 %') +
  theme(legend.position = c(1, 1), 
        legend.justification = c(1, 1))
spectrum.density <-pca.plot$data %>% 
  select(Comp.1, Comp.2, strata) %>% 
  rename(WES = Comp.1, LES = Comp.2) %>% 
  melt(id.vars = "strata", variable.name = "spectrum") %>% 
  ggplot(aes(value, color = spectrum, fill = spectrum)) +
  geom_density(alpha = 0.5) + 
  facet_wrap(~strata, nrow = 2) +
  coord_flip() +
  scale_fill_manual("PCA axis", 
                    labels = c("WES" = "PCA1", "LES" = "PCA2"),
                    values = c("green", "purple")) +
  scale_color_manual("PCA axis", 
                     labels = c("WES" = "PCA1", "LES" = "PCA2"),
                     values = c("green", "purple"))
cowplot::plot_grid(pca.plot, spectrum.density, rel_widths = c(2,1))
```

@@

```{r pcaBRIDGE, fig.cap='Principal Component Analysis (PCA) of species mean trait values for Amazonian species (BRIDGE dataset). Marginal plots represent the density distribution of species on the two principal component axis for each strata.'}
dlim = 0.35
BRIDGE <- readr::read_tsv("./data/species_TROLL_Nino.txt") %>% 
  mutate(strata = ifelse(dmax > dlim, "C", "U"))
BRIDGE.pca <- princomp(~ LMA + Nmass + Pmass + wsg, data = BRIDGE, cor = T)
pca.plot <- autoplot(BRIDGE.pca, 
         data = BRIDGE,
         colour = "strata",
         size = "Freg",
         loadings.label.size = 6,
         loadings.label.colour = 'black',
         loadings = T, loadings.label = T, loadings.colour = 'black',
         loadings.label.vjust = 1.2) +
    coord_equal() +
  geom_hline(aes(yintercept = 0), col = 'green', linetype = "dotted") +
  geom_vline(aes(xintercept = 0), col = 'purple', linetype = "dotted") +
  xlab('Axe 1 − 33.66 %') + ylab('Axe 2 − 29.07 %') +
  theme(legend.position = c(1, 1), 
        legend.justification = c(1, 1))
spectrum.density <- pca.plot$data %>% 
  select(Comp.1, Comp.2, strata) %>% 
  rename(WES = Comp.1, LES = Comp.2) %>% 
  melt(id.vars = "strata", variable.name = "spectrum") %>% 
  ggplot(aes(value, color = spectrum, fill = spectrum)) +
  geom_density(alpha = 0.5) + 
  facet_wrap(~strata, nrow = 2) +
  coord_flip() +
  scale_fill_manual("PCA axis", 
                    labels = c("WES" = "PCA1", "LES" = "PCA2"),
                    values = c("green", "purple")) +
  scale_color_manual("PCA axis", 
                     labels = c("WES" = "PCA1", "LES" = "PCA2"),
                     values = c("green", "purple"))
data <- pca.plot$data %>% 
  select(Comp.1, Comp.2, strata) %>% 
  rename(WES = Comp.1, LES = Comp.2) %>% # ! test !
  melt(id.vars = "strata", variable.name = "spectrum")
Variance <- list(
  LES = list(
    C = round(var(data[data$strata == "C" & data$spectrum == "LES", "value"], na.rm = T), 3),
    U = round(var(data[data$strata == "U" & data$spectrum == "LES", "value"], na.rm = T), 3)),
 WES = list(
   C = round(var(data[data$strata == "C" & data$spectrum == "WES", "value"], na.rm = T), 3),
   U = round(var(data[data$strata == "U" & data$spectrum == "WES", "value"], na.rm = T) ,3))
)
Leven_test <- list(
  C = round(car::leveneTest(value ~ spectrum, data[data$strata == "C",])$`Pr(>F)`[1], 3),
  U = round(car::leveneTest(value ~ spectrum, data[data$strata == "U",])$`Pr(>F)`[1], 3)
)
cowplot::plot_grid(pca.plot, spectrum.density, rel_widths = c(2,1))
```

* Canopy species WES vs LES: `r Variance$LES$C` vs `r Variance$WES$C`, Levene's test p-value=`r Leven_test$C`
* Understorey species LES vs WES: `r Variance$LES$U` vs `r Variance$WES$U`, Levene's test p-value=`r Leven_test$U`
